Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-22 paper.tex
Clean up blade kinematics figure caption

\caption{\hl {Geometric} angle of attack, relative velocity and torque coefficient
 calculated with a NACA 0020 foil operating at $\lambda=1.9$.}
%please mark (a) and (b), (c) in the figure and label them in the caption
\label{fig:blade-kinematics}
\end{figure}

>>>>

    \caption{Geometric angle of attack \textbf{(a)}, relative velocity
        \textbf{(b)},  and torque coefficient \textbf{(c)} calculated with a NACA
        0020 foil operating at $\lambda=1.9$.}

    \label{fig:blade-kinematics}
\end{figure}
